\documentclass{article}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{bm}
\usepackage{epsfig}
\usepackage{makecell}
\usepackage{setspace}
\usepackage{url}
\usepackage[colorlinks=true,citecolor=blue,urlcolor=cyan,linkcolor=red]{hyperref}
\usepackage[cache=false]{minted}
\usepackage{geometry}

\title{Database System Lab \texttt{\#}2 Report}
\author{515030910647, Jiacheng Yang\\\texttt{kipsora@gmail.com}}

\begin{document}
    \maketitle
    \section{Design Decisions}
        In this project, the major designable part is how to how to evict pages when the buffer is full. In my implementations, for the policy of eviction of pages, Least Frequently Used policy is used in my implementation. Other parts are trivial by referring the docs in the comments and the tutorials on the lab's website.

    \section{API Adaptations}
    	In this lab, all of the adaptions is nothing but some utiltiy functions which is used to make the logic of my codes more clear.

    \section{Missing or Incomplete Elements}
        Currently for Lab 2 I've implemented all of the required parts. And all of the incomplete/remained elements will be completed in future labs.

    \section{Time \& Problems}
        Approximately 12 hours is spent on this project including building environment and reading documentations. And during the process of completing this lab, the most confusing/complicated part is to figure out the details of maintaining the property of B+ Tree. Besides, some of the references/documentations of the usages of the classes are ambiguous, which makes some parts difficult to implement and in this part I've spend many time on it. 

        Additionally, another issue is that the tests are too weak and frequently finding bugs in previous passed parts is common.
\end{document}
